Software Ticket Quality

### 2017-11-20 proposal/mprop.tex
Add bib entry and skeleton for information needs in bug reports paper
Added some comments and structure suggestions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{intro}
briefly explain the context of the project problem

@@

\subsection{A subsection}
Please note your proposal need not follow the included section headings; this is only a suggested structure. Also add subsections etc as required

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Statement of Problem}

Clearly state the problem to be addressed in your forthcoming project.
Explain why it would be worthwhile to solve this problem.

\subsection{Introduction}

\subsection{What was covered and why}

\subsection{How papers were found; what terms were searched for + snowballing}

@@

@@

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plain}
\bibliography{mprop}
\end{document}

>>>>

\usepackage{natbib}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}\label{intro}

% 2 - 3 pages tops

\begin{itemize}
\item Background briefly explain the context of the project problem
\item Problem statement and justification. Clearly state the problem to be addressed in your forthcoming project.
  Explain why it would be worthwhile to solve this problem.

\item Research questions and contributions
\item Structure of the rest of the document
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% 10 - 12 pages

@@

\subsection{Study Design}

What was covered and why; How papers were found; what terms were searched for + snowballing.

@@

2nd and 3rd papers both investigate what quality means.

Several authors have investigated the \emph{meaning} of quality.   \cite{sucansuch2018} said ..

Several authors have investigated the application quality metrics to ticket data.

\citet{bachmann2009software} attempted to compute quality metrics for a range of project data sources, including bug tracking databases, version control logs.  They attempted to link bug tracking and change logs and showed that the closed source project investigated reported higher quality metrics.

\citet{}

@@

\textbf{Information needs in bug reports: improving cooperation between developers and users}\cite{breu2010information}:
\begin{itemize}
  \item \textbf{What were the goals?}

  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}

@@

% 3- 4 pages

What are we actually going to do?

Research questions, outline experimental design, independent variables, dependent variables.

@@

% 1 - 2 pages  structure as work packages (don't bother with a chart).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{mprop}
\end{document}
